### 2022-11-15 NSF2022/Description/backgroundv3.tex
...
yuans and bryans changes done

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to
the unit normal pointing into $\Omega(t)$.

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = -pI + \mu(\nabla \uu + \nabla \uu^T),\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2I - \epsilon \nabla \phi \nabla \phi^T\right)
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 2$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\begin{wrapfigure}[10]{l}{0.5\textwidth}
\vspace{-5pt}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic simulations is their fidelity to
physics. The model contains a few parameters; granule radius $c$, decay
length $\epsilon$, surface tension $\gamma$. When these are set to
realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
quantitatively recover well-known elastic moduli for
single-component lipid bilayers \cite{Nagle17, Nagle17-2,
LeVeWa14,NAGLE2000159}. Such agreement is a validation that
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
the long-range interactions between amphiphilic granules (such as lipid
macromolecules) surfaces.
\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-0pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\vspace{-25pt}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

@@

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[17]{r}{3.1in}
  \vspace{-8pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
develop because of the complicated and unbounded domain. This challenge
is compounded when dense suspensions are considered.
Integral equations
(IEs) offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
conditions. Additional advantages of discretizations of IE formulations
include high-order, or even spectral, accuracy and well-conditioned
linear systems that can be solved iteratively with a mesh-independent
number of Krylov iterations such as the generalized minimal residual
method (GMRES). However, IEs have challenges: nearly touching granules
requires a quadrature rule for nearly-singular integrals, their
discretization results in dense matrices, and they cannot immediately be
applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
of tools the IE community, including PI Quaife, has developed to address
these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by solvent phase transitions to the
boundary. It states that energy is always lost as viscous
dissipation. The derivation of~\eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
Transport Theorem to write the time derivative of $E$ as an energy
density flux through the boundary involving the phase stress $T_i$, and
a bulk term involving the Euler-Lagrange derivative of
$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
general evolution of $E$ from the self-assembly process to the
collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[16]{r}{4in} 
  \vspace{-10pt}
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-25pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
\end{wrapfigure}

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. The PIs' recent collaborative
works~\cite{FuQuRyYo22, fu-ryh-qua-you2022}
are a solid foundation for the proposed research.
Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.

>>>>

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid occupying the region $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to
the unit normal pointing into $\Omega(t)$.

To determine how the granules move through space, we seek rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics comes from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif S = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif S = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = -pI + \mu(\nabla \uu + \nabla \uu^T),\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2I - \epsilon \nabla \phi \nabla \phi^T\right)
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case such as $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+b_1 x + b_2$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation,
where $b_1$ and $b_2$ are chosen so that the local minima satisfy
$\phi_0 < 0 < \phi_1$ and $W(\phi_0) = 0$. Section
\ref{sec:specificaim1} discusses certain modifications needed
for~\eqref{eqn:phase} in the nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\begin{wrapfigure}[10]{l}{0.5\textwidth}
\vspace{-5pt}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic simulations is their fidelity to
physics. The model contains a few parameters; granule radius $c$, decay
length $\epsilon$, and surface tension $\gamma$. When these are set to
realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
quantitatively recover well-known elastic moduli for
single-component lipid bilayers \cite{Nagle17, Nagle17-2,
LeVeWa14,NAGLE2000159}. Such agreement is a validation that
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
the long-range interactions between amphiphilic granules (such as lipid
macromolecules) on surfaces.
\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-0pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\vspace{-25pt}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

@@

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[17]{r}{3.1in}
  \vspace{-8pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while an IE method ({\em top right}) requires meshing only
  the boundary of the domain.  ({\em bottom}) An IE method can handle
  intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
develop because of the complex and unbounded domain. This challenge
is compounded when dense suspensions are considered.
Integral equations
(IEs) offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
conditions. Additional advantages of discretizations of IE formulations
include high-order, or even spectral, accuracy and well-conditioned
linear systems that can be solved iteratively with a mesh-independent
number of Krylov iterations such as the generalized minimal residual
method (GMRES). However, IEs have challenges: nearly touching granules
requires a quadrature rule for nearly-singular integrals, their
discretization results in dense matrices, and they cannot immediately be
applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
of tools the IE community, including PI Quaife, has developed to address
these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by solvent phase transitions to the
boundary. It states that energy is always lost as viscous
dissipation. The derivation of~\eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
Transport Theorem to write the time derivative of $E$ as an energy
density flux through the boundary involving the phase stress $T_i$, and
a bulk term involving the Euler-Lagrange derivative of
$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes
equations~\eqref{eqn:stokes}.
Furthermore, while the integral of the phase stress vector
field $T_i\nnu$ over $\Gamma_i$ yields the force on
each granule, the sum of these forces is zero. 
Figure~\ref{fig:coarsening} summarizes the
general evolution of $E$ from the self-assembly process to the
collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[16]{r}{4in} 
  \vspace{-10pt}
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-25pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:stressbalance} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
\end{wrapfigure}

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation, and
modeling for soft-matter systems and foster training in Mathematical
Sciences.
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. The PIs' recent collaborative
works~\cite{FuQuRyYo22, fu-ryh-qua-you2022}
are a solid foundation for the proposed research.
Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.
Sections~\ref{sec:prior} and~\ref{sec:manage} summarize prior support
and project management.

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yuans and bryans changes done

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
undergraduate researchers (URs) per year at Fordham University---for
eight summer weeks. The URs will collaborate directly with the PIs,
receive tutorials (e.g., numerical methods), and be guided on
mathematical writing and presentation. Fordham Mathematics recently
completed a collaboration studio purpose-built for UR support. Work
products include a summary manuscript, a presentation in the Fordham
Undergraduate Research Symposium and departmental seminars, and
participation in a national conference. We have outlined three projects
for the present proposal:
\begin{enumerate}[noitemsep,topsep=0pt]
  \item Translate project code from MATLAB into a compiled language;
  \item Use machine learning and visualizations to post-process data of
    granule dynamics;
  \item Mathematical modeling of collective behavior in social sciences.
\end{enumerate}
PI Ryham has worked side-by-side with dozens of undergraduates and
high-schoolers in supported summer research, Girls in Science Technology
and Mathematics, and the Clare Boothe Luce Scholarship program and the
activity benefited their careers in machine learning, water resources
engineering, threat detection, and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on polling
accessibility in New York City. The PI is finishing works on energy
densities for lipid bilayers with a recently graduated UR, now working
at Raytheon Technologies. His publications include works with seven
undergraduate coauthors~\cite{Figueroa2012CuttingCI, RYHAM20112929,
RyWaCo13, RyKlYaCo16}.

@@

PI Young has been actively involved with promotion of underrepresented
students at NJIT. A former PhD student, Herve Nganguia, is African
American and now an Assistant Professor at Towson University. PI Quaife
is currently advising three female PhD students, and one is African
American and the recipient of the McKnight Doctoral Fellowship which
addresses the underrepresentation of African American and Hispanic
faculty at colleges and universities in the state of Florida. PI Quaife
will also continue to work with undergraduates and high school students
through the Undergraduate Research Opportunity Program and Young
Scholar's Program.

>>>>

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
summer undergraduate researchers (URs) per year at Fordham University for
eight weeks. The URs will collaborate directly with the PIs,
receive tutorials (e.g., numerical methods), and be guided on
mathematical writing and presentation. Fordham Mathematics recently
completed a collaboration studio purpose-built for UR support. Work
products include a summary manuscript, a presentation in the Fordham
Undergraduate Research Symposium and departmental seminars, and
participation in a national conference. We have outlined three projects
for the present proposal:
\begin{enumerate}[noitemsep,topsep=0pt]
  \item Translate project code from MATLAB into a compiled language;
  \item Use machine learning and visualizations to post-process data of
    granule dynamics;
  \item Mathematical modeling of collective behavior in social sciences.
\end{enumerate}
PI Ryham has worked side-by-side with dozens of undergraduates and
high-schoolers in supported summer research, Girls in Science Technology
and Mathematics, and the Clare Boothe Luce Scholarship program and the
activity benefited their careers in machine learning, water resources
engineering, threat detection, and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on polling
accessibility in New York City. The PI is finishing works on energy
densities for lipid bilayers with a recently graduated UR, now working
at Raytheon Technologies. His publications include works with seven
undergraduate coauthors~\cite{Figueroa2012CuttingCI, RYHAM20112929,
RyWaCo13, RyKlYaCo16}.

@@

PI Young has been actively involved with promotion of underrepresented
students at New Jersey Institute of Technology. A former PhD student,
Herve Nganguia, is African American and now an Assistant Professor at
Towson University. PI Quaife is currently advising three female PhD
students, and one is African American and the recipient of the McKnight
Doctoral Fellowship which addresses the underrepresentation of African
American and Hispanic faculty at colleges and universities in Florida.
PI Quaife will also continue to work with undergraduates and high school
students through the Undergraduate Research Opportunity Program and
Young Scholar's Program at Florida State University.
